```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, comment = NA, message = FALSE)
## Packages that must be installed in R, to run this:
library(aplpack)
library(ggplot2)
library(knitr)
options(width = 100)
```

# THE DATA USED IN THIS REPORT

## The marks folder and its contents

The **full path** to the marks folder used in this report is:
```{r report_the_data_path}
marks_folder <- paste0(working_directory, "/marks")
norman::print_path(marks_folder)
```

The **data files contained in that folder** are: 
```{r show_the_folder_list, results="asis"}
filenames <- norman::print_file_listing(marks_folder)
```

```{r read_in_the_marks, include=FALSE, echo=FALSE}
module_codes <- unlist(substr(filenames, 1, 5))
module_marks <- vector(mode = "list", length = length(module_codes))
for (i in seq(along = filenames)) {
    module_marks[[module_codes[i]]] <-
        read.csv(paste0(marks_folder, "/", 
                        filenames[i]))[, c("sprCode", "overallMark")]
}
student_IDs <- sapply(module_marks, function(m) as.character(m[[1]]))
module_marks <- sapply(module_marks, function(m) (m[[2]]))
unique_student_IDs <- sort(unique(unlist(student_IDs)))
marks_matrix <- matrix(NA, length(unique_student_IDs), length(module_codes))
rownames(marks_matrix) <- unique_student_IDs
colnames(marks_matrix) <- module_codes
for (m in module_codes) {
  marks_matrix[student_IDs[[m]], m] <- module_marks[[m]]
}
```

## Basic checks on the data 

```{r check_modules_expected, include=FALSE}
checklist <- norman::check_modules_expected(working_directory, module_codes)
```

```{r check_module_names, include=FALSE}
if (file.exists(paste0(working_directory, "/module_names.csv"))) {
  module_names <- read.csv(paste0(working_directory, "/module_names.csv"))
  row.names(module_names) <- module_names[, 1]
  module_names$ModuleCode <- NULL
  missing_module_names <- module_codes[!module_codes %in% row.names(module_names)]
  if (length(missing_module_names) == 0) missing_module_names <- "none"
} else {
    module_names <- NULL
    missing_module_names <- "**ERROR**, the file \\small `module_names.csv` \\normalsize does not exist"
}
```

Modules expected that were **missing from the marks folder**: 
`r paste(checklist$missing)`

Modules that were **found in the marks folder unexpectedly**: 
`r paste(checklist$extras)`

**Module names missing** from \small `module_names.csv`\normalsize: `r paste(missing_module_names)`


# SUMMARY OF ALL MODULES

**Overall median mark: `r median(marks_matrix, na.rm = TRUE)`**

## Seven-number summaries

```{r summary_all_modules}
summaries <- norman::raw_mark_summaries(marks_matrix)
kable(summaries)
```

## Percentages in degree-class ranges

```{r classes_all_modules}
classes <- norman::raw_mark_classes(marks_matrix)
kable(classes)
rownames(classes) <- paste(rownames(classes), "(%)")
```

\newpage


# MODULE EFFECTS

Module effects are measured via a two-stage analysis:

1. For every possible pair of modules, calculate the **median of the differences in marks** (across the students who took both modules).
2. Find, by weighted least squares, the **vector of module effects that best fits** those median differences.

This analysis is similar to Tukey's _median polish_ analysis, but is both more transparent and more robust for the present purpose.  (Blog post at https://statgeek.net/2019/04/26/robust-measurement-from-a-2-way-table/ amplifies this a little.)

For completeness, in case needed, the median differences from stage 1 are reported in full, in the next sub-section.

**The result of this median-of-differences analysis is the following table of module effects.**  The effects are centred such that their mean is zero.  Also reported in the table is the total number of within-student differences that were available to use in this analysis, for each module.


```{r compute-median-differences, include = FALSE}
md <- norman::meddiff(marks_matrix)  ## used as input to meddiff_fit()
mdd <- norman::meddiff_for_display(marks_matrix)
## the latter is used only for the full listing of differences below
mdfit <- norman::meddiff_fit(md)
rsq <- summary(mdfit)$r.squared
```


## The computed module effects

Easiest to hardest.  All are **relative to the average module**. 

Also shown here, for each of the modules, is the total number (Count) of mark-pair comparisons that were available for that module.

(The average Effect is set to zero, _arbitrarily_: in this analysis it is only the _differences_ between modules that are interpretable.   The specific average used for this is the _weighted_ mean, the weights being the numbers shown in the _Count_ column.  This prevents small modules from having an undue influence on how the Effect values are centred --- for presentation purposes --- in the table below.)

```{r report_the_module_effects, results="asis"}
mdf <- norman::get_module_effects(module_codes, mdd)
```

These module effects explain `r paste0(round(100 * rsq, 0), "%")` of the variation among the median differences listed below.


## The full list of median differences

These are listed here for completeness, just in case any of them needs to be looked at (in the scaling meeting, for example).

For each considered module, tabulated here are all _other_ modules that were taken (by at least one student) together with the module under consideration.  For each such 'comparator' module, two numbers are shown here:

1. The **median difference** between students' scores for the two modules (rounded to integer where needed).  Positive values indicate a comparator module that was found to be harder than the module under consideration; and the opposite for negative values.
2. The **count** of students who took both modules.

\small

```{r list_all_median_differences}
norman::list_all_median_differences(mdd)
```

\normalsize

\newpage


# INDIVIDUAL MODULE SUMMARIES

```{r make_overall_means, include = FALSE}
student_overall_mean <- rowMeans(marks_matrix, na.rm = TRUE)
```

```{r make-module-pages, include = FALSE}
module_pages <- norman::make_module_pages(working_directory,
                                          module_codes, module_names)
```

```{r print-module-pages, results="asis"}
cat(module_pages, collapse = "\n")
```
